### 2024-08-18 paper.tex
finish Jordan basis

    \end{proof}
\end{proof}
\par We list the chains of the Jordan basis.
First, for each \(i \notin I\), we take the chain of length \(p_i + q_i\) beginning with \(e_{i,p_i + q_i} = e_{i\lambda_i}\).
\par Now, it is clear that each \(f_i\) is in the span of the chains we have listed so far.
It is also clear that \(b \leftshift k\) is in the span, for each \(k \geq 0\).
\par Now, we handle the \(i\) with \(q_i < n\).
We take as an inductive hypothesis that for all \(i' < i\) and all \(j\), we have \(e_{i'j}\) in the span of the chains we have already listed.
\par If \(p_i \leq \max_{k > i} p_k\), then we take the chain beginning with \(e_{i,p_i + q_i}\) of length \(p_i + q_i\).
Clearly we then have \(e_{i'j}\) in the span of the chains we have listed, for \(i' \leq i\).
\par Now, we want to show that for each \(j\), \(e_{ij}\) is in the span of the chains we've listed so far.
Since \(A^{q_i + \max_{k > i} p_k} v_i\) has rows \(k\) zeroed out for \(k \geq i\), our inductive hypothesis tells us that \(A^{q_i + \max_{k > i} p_k} v_i \rightshift q_i + \max_{k > i} p_k\) is in the span of the chains already listed.
So it suffices to show that the closure of \(\langle v_i \rangle\) under action by \(A\) contains the span of \(e_{ij}\).
And \(A^{n - q_i} f_n\) is also in the span of chains already listed, so it suffices to show that the closure of \(\langle \sum_k b_{ik} e_{i,k + q_i}\rangle \) under action by \(A\) contains \(\langle e_{ij}\rangle\).
And this just follows from the fact that \(b_{i,p_i}\) is nonzero.
\par Now, I've shown that my purported Jordan basis has a large enough span; to show that it is indeed a Jordan basis I just need to count the number of vectors and show that we obtain \(m + n\).
I list the purported basis here:
\begin{itemize}
    \item TODO
\end{itemize}
Indeed, the sum of the lengths is
\[\left[\sum_{i : q_i \geq n + r} (p_i + q_i)\right] + (r + n + \max_{i : q_i < n + r} p_i) + \sum_{i : q_i < n + r} \begin{cases}
    p_i + q_i, & p_i \leq \max_{k > i} p_k \\
    q_i + \max_{k > i} p_i, & p_i > \max_{k > i} p_k
\end{cases} = \]
\[\left[\sum_{i : q_i \geq n + r} (p_i + q_i)\right] + (r + n + \max_{i : q_i < n + r} p_i) + \sum_{i : q_i < n + r} (q_i + \min(p_i, \max_{k > i} p_i)).\]
Let \(i_1 < \cdots < i_s\) be the `peaks': that is, the set \(I_1 = \{i : q_i < n + r \land p_i > \max_{k > i} p_k\}\).
(As I should've mentioned before, we take the max of the empty set to be zero.)
Let \(I_2 = \{i : q_i < n + r\} \setminus I_1\).
Then 
\[\sum_{i : q_i < n + r} (q_i + \min(p_i, \max_{k > i} p_i)) = \sum_{i \in I_2} (p_i + q_i) + \sum_{k = 1}^s (q_{i_k} + p_{i_{k + 1}}).\]
Clearly then, the whole sum is \(m + n\).

>>>>

    \begin{proof}[Proof of (3)]
        Let \(W\) be the span of the chains listed.
        We need to show that \(W = \mathbb{C}^{m + n}\).
        Because every \(i \in I\) satisfies \(q_i < n\), clearly \(\langle e_{ij}\rangle_{i,j : q_i \geq n} \subseteq W\).
        \par I claim that \(f_n \in W\) as well.
        To see this, we consider the chain beginning with \(f_n - (A^{n + P} f_n \rightshift n + P)\).
        As explained in the proof of (1), we have \(A^{n + P} f_n \in \langle e_{ij}\rangle_{i,j : q_i \geq n}\).
        Consequently, \((A^{n + P} f_n \rightshift n + P) \in \langle e_{ij} \rangle_{i,j : q_i \geq n} \subseteq W\).
        Because \(f_n - (A^{n + P} f_n \rightshift n + P) \in W\), this implies that \(f_n \in W\).
        \par Because \(AW \subseteq W\) (obvious, since \(W\) is the span of chains), the fact that \(f_n \in W\) implies that \(f_i \in W\) for each \(i\), and also \(b \leftshift l \in W\) for each \(l \geq 0\).
        \par Now we are left with showing that \(\langle e_{ij} \rangle_{i,j : q_i < n} \subseteq W\).
        This is obvious for \(i \notin I\).
        For \(i \in I\), we do it inductively.
        Fix \(i \in I\), and suppose we have already shown that for all \(i' \in I\) with \(q_{i'} > q_i\), we have \(\langle e_{ij} \rangle_{j \textrm{ arbitrary}} \subseteq W\).
        We will show that \(\langle e_{ij} \rangle_{j \textrm{ arbitrary}} \subseteq W\).
        \par To see this, we consider the chain beginning with \(v_i - (A^{q_i + P_i} v_i \rightshift q_i + P_i)\).
        (Recall \(v_i = A^{n - q_i} f_n - \sum_{l = 1}^{p_i} b_{il} e_{i,l + q_i}\).)
        Because \(AW \subseteq W\), and \(b_{i,p_i} \neq 0\) (by definition of \(p_i\)), it suffices to show that \(\sum_{l = 1}^{p_i} b_{il} e_{i,k + q_i} \in W\).
        As explained in the proof of (1), we have \(A^{q_i + P_i} v_i \in \langle e_{lj} \rangle_{q_l \geq q_i}\).
        And since \(A^{q_i + P_i} v_i\) has row \(i\) zeroed out, in fact \(A^{q_i + P_i} v_i \in \langle e_{lj} \rangle_{l : l \neq i \land q_l \geq q_i}\).
        Hence, \(A^{q_i + P_i} v_i \rightshift q_i + P_i \in \langle e_{lj} \rangle_{l : l \neq i \land q_l \geq q_i}\).
        By our inductive hypothesis, \(\langle e_{lj} \rangle_{l : l \neq i \land q_l \geq q_i} \subseteq W\), and consequently \(A^{q_i + P_i} v_i \rightshift q_i + P_i \in W\).
        Since we know \(v_i - (A^{q_i + P_i} v_i \rightshift q_i + P_i) \in W\), this implies that \(v_i \in W\).
        Because \(A^{n - q_i} f_n \in W\), this then implies that \(\sum_{l = 1}^{p_i} b_{il} e_{i,l + q_i} \in W\), as desired.
    We proved (1), (2), (3), so we are done.
